ripplerestr
===========

Use **R** with the [`ripple-rest`](https://dev.ripple.com/) API.

Introduction
------------

[Ripple](https://ripple.com/) is an Internet protocol for making financial transactions.

The [`ripple-rest`](https://dev.ripple.com/) API makes it easy to access the Ripple system via a RESTful web interface.

The **R** package [`ripplerestr`](https://github.com/hmalmedal/ripplerestr) uses the [`httr`](https://github.com/hadley/httr) library to communicate with `ripple-rest`.

Prerequisites
-------------

Before you can use the `ripple-rest` API, you will need to have three things:

 * An installed version of `ripple-rest` running locally or remotely. Instructions on installing `ripple-rest` can be found in the README.md file in the [Github repository](https://github.com/ripple/ripple-rest).
 * An activated Ripple account.
 * The URL of the server running the `ripple-rest` API that you wish to use.

Installation
------------

Download the [latest release](https://github.com/hmalmedal/ripplerestr/releases/latest) and install it.

Set up
------

Load the `ripplerestr` library and set the URL.

```{r setup}
library(ripplerestr)
options("ripplerestr.url" = "http://localhost:5990/")
```
```{r cache, echo=FALSE}
opts_chunk$set(cache=TRUE)
```

Check server
------------

Check whether the server is ready to be used.

```{r connected}
is_server_connected()
```

List server information.

```{r status}
get_server_status()
```

Get an account's balances
-------------------------

Find how much USD Bitstamp has issued.

```{r bitstamp}
bitstamp_coldwallet <- "rvYAfWj5gh67oV6fW32ZzP3Aw4Eubs59B"
bitstamp_hotwallet <- "rrpNnNLKrartuEqfJGpqyDwPj1AFPg9vn1"
bitstamp_coldUSD <- get_account_balances(bitstamp_coldwallet, "USD")
bitstamp_hotUSD <- get_account_balances(bitstamp_hotwallet, "USD")
bitstamp_USD <- sum(bitstamp_coldUSD) + sum(bitstamp_hotUSD)
bitstamp_USD
```

